Place of death in NRS COVID-19 deaths: data processing for analysis, 2023 data

### 2023-02-22 covid_nrs_place_of_death_data_2023.Rmd
modified output tables to account for 2023 data

    ## 2022 data so far

@@

@@

      period = glue::glue("2022 up to week {weeks_available_2023}"),

@@

>>>>

    ## 2022
        period = "2022",
    ## 2023 data so far

@@

          year == 2023

@@

      period = glue::glue("2023, up to week {weeks_available_2023}"),

@@

# Causes of death over time, proportion inside and between places

Table of number of deaths by cause, place of death and year, showing proportion of deaths by cause within each place `prop_cod_within_pod` (e.g. Covid deaths were 2% of home deaths) and proportion of deaths by place within each cause `prop_pod_within_cod` (e.g. 70% of all Covid deaths happened in hospital).
Note that because historic data was given averaged over the 5 year period, the historic figures are given as a mean over the period rather than an annual total.

```{r}
table_proportions_of_cause_of_death <-
  bind_rows(
    ## historic periods
    historical_annual_average_cause_of_death %>%
      rename(year = historic_period, deaths = annual_deaths_mean),
    ## current data
    total_deaths_cause_of_death %>%
      select(-c(historic_period,annual_deaths_mean:ncol(.))) %>%
      mutate(year = as.character(year))
  ) %>%
  filter(place_of_death!="All" & cause_of_death!="All") %>%
  group_by(year,place_of_death) %>%
  mutate(prop_cod_within_pod = deaths / sum(deaths)) %>%
  group_by(year,cause_of_death) %>%
  mutate(prop_pod_within_cod = deaths / sum(deaths)) %>%
  ungroup %>%
  (function(data_tbl){
    bind_rows(
      data_tbl,
      ## all cause
      data_tbl %>%
        group_by(year, place_of_death) %>%
        summarise(
          cause_of_death = "All",
          deaths = sum(deaths),
          prop_cod_within_pod = 1,
          .groups = "drop"
        ) %>%
        group_by(year, cause_of_death) %>%
        mutate(prop_pod_within_cod = deaths/sum(deaths)) %>%
        ungroup,
      ## all place of death
      data_tbl %>%
        group_by(year, cause_of_death) %>%
        summarise(
          place_of_death = "All",
          deaths = sum(deaths),
          prop_pod_within_cod = 1,
          .groups = "drop"
        ) %>%
        group_by(year, place_of_death) %>%
        mutate(prop_cod_within_pod = deaths/sum(deaths)) %>%
        ungroup
    )
  }) %>%
  mutate(
    year = factor(year, levels = unique(year)),
    cause_of_death = factor(cause_of_death, levels = order_of_causes_of_death),
    place_of_death = factor(place_of_death, levels = order_of_place_of_death_levels[c(5,1,3,2,4)])
    ) %>%
  arrange(year, place_of_death, cause_of_death)

table_proportions_of_cause_of_death %>%
  write_csv(file = paste0(dir_outputs,"/proportions_of_deaths_by_place_&_cause.csv"))
```
